This is the title [Article v\versionnumber]

### 2022-04-07 manuscript/manuscript.tex

%%% Shortcuts and macros
\newcommand{\dgsolv}{\Delta G_\textup{solv}}
\newcommand{\software}{\emph}
\newcommand{\todo}{\textcolor{red}}

@@

\software{gisttools} contains functionality to perform this analysis easily.
There is also a method ``detect\_reference\_value'' that automatically tries to find the converged value fo the rdf.
Although it has a simple convergence check built-in, it is always recommended to check the convergence by hand as well.

\begin{lstlisting}[style=python]
import gisttools as gt
import matplotlib.pyplot as plt
gist = gt.gist.load_gist_file(
    "gist.dat", struct="solute-centered.pdb")
bins, eww = gist.rdf("Eww_unref", bins=100, rmax=20.)
_, n = gist.rdf(
    "population", bins=100, rmax=20., col_suffix="")
plt.plot(
    bins,
    eww / (n/gist.n_frames/gist.grid.voxel_volume))
eww_auto = gist.detect_reference_value().values[0]
plt.axhline(eww_auto, color='k')
plt.gca().set(
    xlabel='distance [A]', ylabel='E_ww per mol')
plt.show()
\end{lstlisting}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{figures/Eww_convergence.eps}
	\caption{Convergence of $E_{ww}$ with increasing distance to the solute. The horizontal line shows the automatically computed reference energy.}
	\label{fig_ewwref}
\end{figure}

\subsection{Visualizing $\dgsolv$}
\subsection{Contribution of Hydration to Binding}

>>>>

%%% Shortcuts and macros
\newcommand{\dgsolv}{\Delta G_\textup{solv}}
\newcommand{\software}{\emph}
\newcommand{\todo}{\textcolor{red}}
\newcommand\inlinecode{\texttt}

@@

\software{gisttools} contains functionality to perform this analysis easily.
There is also a method \inlinecode{detect\_reference\_value} that automatically tries to find the converged value fo the rdf.
Although it has a simple convergence check built-in, it is always recommended to check the convergence by hand as well.

\begin{lstlisting}[style=python]
import gisttools as gt
import matplotlib.pyplot as plt
gist = gt.gist.load_gist_file(
    "gist.dat", struct="solute-centered.pdb")
bins, eww = gist.rdf(
    "Eww_unref", bins=100, rmax=20., normalize="norm")
plt.plot(bins, eww)
eww_auto = gist.detect_reference_value().values[0]
plt.axhline(eww_auto, color='k')
plt.gca().set(
    xlabel='distance [A]', ylabel='E_ww per mol')
plt.show()
\end{lstlisting}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{figures/Eww_convergence.eps}
	\caption{Convergence of $E_{ww}$ with increasing distance to the solute. The horizontal line shows the automatically computed reference energy. Computed from the complex calculation.}
	\label{fig_ewwref}
\end{figure}

After choosing an appropriate reference value, we need to subtract this value from Eww.
Make sure to subtract the reference from the normalized (\_norm) data.
In \software{gisttools}, this is done simply by setting \inlinecode{gist.eww\_ref}.
In \software{gistpp}, this can be done as follows: \todo{This might become invalid with future GIST versions, depending on whether we adopt the COM as molecular center.}

\begin{lstlisting}
rho0=0.03287465
neg_eww_ref=9.533
gistpp -op multconst -i gist-gO.dx -opt const $rho0 \
    -o gist-gO-abs.dx 
gistpp -op div -i gist-Eww-dens.dx -i2 gist-gO-abs.dx \
    -o gist-Eww-norm.dx
gistpp -op addconst -i gist-Eww-norm.dx \
    -opt const $neg_eww_ref -o gist-Eww-ref-norm.dx
gistpp -op mult -i gist-Eww-ref-norm.dx \
    -i2 gist-gO-abs.dx -o gist-Eww-ref-dens.dx
\end{lstlisting}

Now, add all free energy contributions to obtain the spatially resolved $\dgsolv$.
In \software{gisttools}, this is done automatically (simply use the \inlinecode{A\_dens} and \inlinecode{A\_norm} columns).
In \software{gistpp}, use the \inlinecode{add} command, with the same syntax as the \inlinecode{div} command used above.
After that, check whether your free energy contributions become negligible at high distances to the solute.
In a plot like Figure \ref{fig_ewwref} based on the \inlinecode{A\_dens} column, the values should tend to zero.
However, it is more informative to plot the cumulative free energy contribution against the distance to the solute, to check the convergence.
It the curve flattens out, this is your final $\dgsolv$.
If it does not, you might need to tweak the Eww reference, or introduce a reference value for the entropy (especially with older versions of \software{cpptraj}).

\begin{lstlisting}[style=python]
import gisttools as gt
import matplotlib.pyplot as plt
# adapt eww_ref!
gist = gt.gist.load_gist_file("gist.dat",
    struct="solute-centered.pdb", eww_ref=-9.533)
bins, (dg, eww, esw, s) = gist.rdf(
    ["A_dens", "Esw_dens", "Eww_dens", "dTSsix_dens"],
    bins=100, rmax=20., normalize="none")
plt.plot(bins, np.cumsum(dg), label="dG")
plt.plot(bins, np.cumsum(eww), label="Eww")
plt.plot(bins, np.cumsum(esw), label="Esw")
plt.plot(bins, np.cumsum(s), label="dS")
\end{lstlisting}

The expected output of this code is shown in Figure \ref{fig_radial_convergence}.
In this case, both the Eww energy and the entropy are not perfectly flat, indicating that the reference value is not optimal.
The slow energy convergence indicates that a non-optimal reference value was used, but is also complicated by the fact that a charged solute is used without neutralizing counter ions.

\begin{figure}
	\centering
	\includegraphics[width=0.8\linewidth]{figures/A_E_S_convergence.eps}
	\caption{Convergence of $\dgsolv$ and its contributions with increasing distance to the solute. All quantities cumulative, i.e., summed up to the respective radius. Computed from the biotin calculation.}
	\label{fig_radial_convergence}
\end{figure}

\subsection{Visualizing $\dgsolv$}
Next, we want to visualize the 3-dimensional contributions to the free energy of hydration, as well as the entropy and enthalpy contributions.
You can use PyMol\cite{pymol} or VMD\cite{vmd} to visualize the .dx files from GIST.
With \software{gistpp}, you can use the file from the convergence check. Additional OpenDX files can be produced using \inlinecode{gistpp -op makedx}.
With \software{gisttools}, you can create one using e.g., \inlinecode{gist.save\_dx("A\_dens", "A\_dens.dx")}.

Visualize the free energy, the total energy, and the entropy, at several iso-levels.
The expected result is shown in Figure ???.

\subsection{Contribution of Hydration to Binding}
